% Written By Enoch Yu
% Downloaded from archive.enochyu.com

\documentclass{article}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}

\usepackage[margin=1in]{geometry}
\usepackage[dvipsnames]{xcolor}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[L]{AMC 8 Class}
\fancyhead[C]{Problem Set 1}
\fancyhead[R]{Enoch Yu}
\usepackage{lastpage}
\fancyfoot[C]{Page \thepage \hspace{1pt} of \pageref{LastPage}}
\usepackage{parskip}

\newcommand {\MyLine} {
    \smallskip \noindent\rule{\textwidth}{0.4pt} \smallskip
}

\title{Assignment for Orientation}
\author{Enoch Yu}
\date{11 August 2025}


\begin{document}

Name:

Date:

\section*{\textcolor{ForestGreen}{Easy}}
\begin{minipage}[t][0.4\textheight][t]{\textwidth}
\subsection*{Problem 1.} % 2023 AMC 8 Problem 1 (18)
{\color {Gray}
Compute: $(8 \times 4 + 2) - (8 + 4 \times 2)$.
}

\MyLine

\textbf{Solution.}

\end{minipage}


\begin{minipage}[t][0.4\textheight][t]{\textwidth}
\subsection*{Problem 2.} % 2019 AMC 8 Problem 3 (2, 3, 1)
{\color {Gray}
Order the fractions $\frac{15}{11}$, $\frac{19}{15}$,
and $\frac{17}{13}$ from least to greatest.
}

\MyLine

\textbf{Solution.}

\end{minipage}


\newpage
\section*{\textcolor{YellowOrange}{Moderate}}
\begin{minipage}[t][0.45\textheight][t]{\textwidth}
\subsection*{Problem 3.} % 2016 AMC 8 Problem 10 (10)
{\color {Gray}
Define $a * b$ as $3a - b$. Find the value of $x$ if
\[
2 * (5 * x) = 1.
\]
}

\MyLine

\textbf{Solution.}

\end{minipage}

\begin{minipage}[t][0.45\textheight][t]{\textwidth}

\subsection*{Problem 4.} % 2023 BmMT Individual Problem 3 (12)
{\color {Gray}
Three positive integers $x$, $y$, and $z$ satisfies
the following equation.
\[
x + \frac{y}{z} = \frac{11}{6}
\]
Find the minimum value of $x + y + z$.
}

\MyLine

\textbf{Solution.}

\end{minipage}

\section*{\textcolor{BrickRed}{Challenging}}
\begin{minipage}[t][0.45\textheight][t]{\textwidth}
\subsection*{Problem 5.} % 2023 AMC 10A Problem 12 (14)
{\color {Gray}
Let $N$ be a three-digit positive integer that is
divisible by $7$. The number formed by reversing
the digits of $N$ is divisible by $5$. How many
$N$'s are there?
}

\MyLine

\textbf{Solution.}

\end{minipage}

\begin{minipage}[t][0.45\textheight][t]{\textwidth}
\subsection*{Problem 6.} % 2018 AMC 10A Problem 16 (13)
{\color {Gray}
Let there be a right triangle $ABC$ with side lengths
of $AB = 20$ and $BC = 21$. Including $\overline{AB}$
and $\overline{BC}$, how many line segments with
integer length can be drawn from vertex $B$ to a point
on hypotenuse $\overline{AC}$?
}

\MyLine

\textbf{Solution.}

\end{minipage}

\end{document}

