% Written By Enoch Yu
% Downloaded from archive.enochyu.com

\documentclass{article}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}

\usepackage[margin=1in]{geometry}
\usepackage[dvipsnames]{xcolor}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[L]{AMC 8 Class}
\fancyhead[C]{Problem Set 2}
\fancyhead[R]{Enoch Yu}
\usepackage{lastpage}
\fancyfoot[C]{Page \thepage \hspace{1pt} of \pageref{LastPage}}
\usepackage{parskip}

\newcommand {\MyLine} {
    \smallskip \noindent\rule{\textwidth}{0.4pt} \smallskip
}

\title{Problem Set 2}
\author{Enoch Yu}
\date{18 August 2025}

\begin{document}

Name:

Date:

\section*{\textcolor{ForestGreen}{Easy}}
\begin{minipage}[t][0.4\textheight][t]{\textwidth}
\subsection*{Problem 1.} % 2025 AMC 8 Problem 4 (37)
{\color {Gray}
Mr. Jian is counting backward by $7$s starting
from $100$ (i.e. $100, 93, 86, \ldots$). What is
his $10^\text{th}$ number?
}

\MyLine

\textbf{Solution.}

\end{minipage}


\begin{minipage}[t][0.4\textheight][t]{\textwidth}
\subsection*{Problem 2.} % 2022 AMC 8 Problem 3 (4)
{\color {Gray}
When three positive integers $a$, $b$, and $c$
are multiplied together, their product is $100$.
Suppose $a < b < c$. In how many ways can the numbers
be chosen?
}

\MyLine

\textbf{Solution.}

\end{minipage}


\newpage
\section*{\textcolor{YellowOrange}{Moderate}}
\begin{minipage}[t][0.45\textheight][t]{\textwidth}
\subsection*{Problem 3.} % 2022 AMC 8 Problem 13 (9)
{\color {Gray}
How many positive integers can fill the blank in the
sentence below?

``One positive integer is $\underline{\qquad}$ more
than twice another, and the sum of the two numbers is
$28$.''
}

\MyLine

\textbf{Solution.}

\end{minipage}

\begin{minipage}[t][0.45\textheight][t]{\textwidth}

\subsection*{Problem 4.} % 2022 AMC 8 Problem 14 (24)
{\color {Gray}
In how many ways can the letters in $\textbf{BEEKEEPER}$
be rearranged so that two or more $\textbf{E}$s do
not appear together?
}

\MyLine

\textbf{Solution.}

\end{minipage}

\section*{\textcolor{BrickRed}{Challenging}}
\begin{minipage}[t][0.45\textheight][t]{\textwidth}
\subsection*{Problem 5.} % 2022 AMC 10A Problem 14 (144)
{\color {Gray}
How many ways are there to split the integers $1$
through $14$ into $7$ pairs such that in each pair,
the greater number is at least $2$ times the lesser
number?
}

\MyLine

\textbf{Solution.}

\end{minipage}

\begin{minipage}[t][0.45\textheight][t]{\textwidth}
\subsection*{Problem 6.} % 2000 AMC 10 Problem 20 (69)
{\color {Gray}
Let $A$, $M$, and $C$ be nonnegative integers such
that $A+M+C=10$. What is the maximum value of
$A\cdot M\cdot C+A\cdot M+M\cdot C+C\cdot A$?
}

\MyLine

\textbf{Solution.}

\end{minipage}

\end{document}

