% Written By Enoch Yu
% Downloaded from archive.enochyu.com

\documentclass{article}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}

\usepackage[margin=1in]{geometry}
\usepackage[dvipsnames]{xcolor}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[L]{AMC 8 Class}
\fancyhead[C]{Problem Set 3}
\fancyhead[R]{Enoch Yu}
\usepackage{lastpage}
\fancyfoot[C]{Page \thepage \hspace{1pt} of \pageref{LastPage}}
\usepackage{parskip}

\newcommand {\MyLine} {
    \smallskip \noindent\rule{\textwidth}{0.4pt} \smallskip
}

\title{Problem Set 3}
\author{Enoch Yu}
\date{25 August 2025}

\begin{document}

Name:

Date:

\section*{\textcolor{ForestGreen}{Easy}}
\begin{minipage}[t][0.4\textheight][t]{\textwidth}
\subsection*{Problem 1.} % Made by Enoch (17*73)
{\color {Gray}
Prime factorize $1343$.
}

\MyLine

\textbf{Solution.}

\end{minipage}


\begin{minipage}[t][0.4\textheight][t]{\textwidth}
\subsection*{Problem 2.} % Made by Enoch (180(100-2)/100)
{\color {Gray}
Find the sum of all interior angle of a regular
polygon with $100$ sides.
}

\MyLine

\textbf{Solution.}

\end{minipage}


\newpage
\section*{\textcolor{YellowOrange}{Moderate}}
\begin{minipage}[t][0.45\textheight][t]{\textwidth}
\subsection*{Problem 3.} % Made by Enoch (-500)
{\color {Gray}
Compute the sum:
\[
2 - 4 + 6 - 8 + \cdots - 1000.
\]
}

\MyLine

\textbf{Solution.}

\end{minipage}

\begin{minipage}[t][0.45\textheight][t]{\textwidth}

\subsection*{Problem 4.} % Made By Enoch (10)
{\color {Gray}
Minha, Diana, Isabel, John, and Mr. Jian are at a
party. Each attendance is asked to shake hands with
other peers in the party. How many handshakes are
there?
}

\MyLine

\textbf{Solution.}

\end{minipage}

\section*{\textcolor{BrickRed}{Challenging}}
\begin{minipage}[t][0.45\textheight][t]{\textwidth}
\subsection*{Problem 5.} % Made By Enoch
{\color {Gray}
Prove that an interior angle of a regular $n^\text{th}$
polygon is $\dfrac{180^\circ (n - 2)}{n}$.
}

\MyLine

\textbf{Solution.}

\end{minipage}

\begin{minipage}[t][0.45\textheight][t]{\textwidth}
\subsection*{Problem 6.} % Made By Enoch
{\color {Gray}
Find the explicit formula for the number of factors
of all numbers in the form of $p_1^{a_1} p_2^{a_2}
p_3^{a_3}$ where $p_1, p_2, p_3$ are prime numbers
and $a_1, a_2, a_3$ are positive integers.
}

\MyLine

\textbf{Solution.}

\end{minipage}

\end{document}


